Democratic Algorithm (DA) : A Novel Approach to Hierarchical Swarm Intelligence\\

### 2020-09-29 VLSID/paper.tex
Draft_4

\begin{proof}\renewcommand{\qedsymbol}{}
Let $X$ = $\{X\textsuperscript{1}, X\textsuperscript{2} \dots, X\textsuperscript{n} \}$ be the candidates and $a\textsubscript{i}$ and $b\textsubscript{i}$ be the candidate and solutino incidence vectors. \\
\begin{align*}
d(A,B) &= \sum_{i=1}^{n}(a\textsubscript{i} + b\textsubscript{i} - 2a\textsubscript{i}b\textsubscript{i})\\
 &= \sum_{i=1}^{n}[(1-b\textsubscript{i})a\textsubscript{i} + (1-a\textsubscript{i})b\textsubscript{i}]\\
 &= \sum_{i=1}^{n}|a\textsubscript{i} - b\textsubscript{i}| = ||a - b||\textsubscript{1}
\end{align*}
\end{proof}
Therefore the Hamming Distance between the incidence vectors can act as a metric for mapping. A secondary measure utilized in the mapping is $\delta\textsubscript{B}(A)$ = $|A| - |A \cap B|$ which counts the number of candidates in set $A$ but not in set $B$. Stochastic convergence proof is discussed next.

@@

The implication of $d(F\textsubscript{t}, M\textsuperscript{*}) \rightarrow 0$ implies $\delta\textsubscript{M\textsuperscript{*}}(F\textsubscript{t}) \rightarrow 0$ extends to the worst case scenario of $n = M\textsuperscript{*}$. However, if a Markov Chain is maintained dynamically, $|M\textsuperscript{*}|=1$ and the limited population size will stagnate to a critical point. 
% From a mathematical point of view, both the structure and the search processes evolve over time with feedback. For each search, a lookup is conducted by candidate $\textit{c}$ in table $\textit{H}$. If not found, a solution $\textit{x\textsubscript{0}}$ is assumed as the initial point and the search of optimum solution $\textit{x\textsubscript{1}}$ begins. At the end of each expedition, the top department's performance is graded through a reward system. Based on the global performance overall a set runtime, either the department continues in power or gets replaced.

>>>>

\begin{proof}\renewcommand{\qedsymbol}{}
Let $X$ = $\{X\textsuperscript{1}, X\textsuperscript{2} \dots, X\textsuperscript{n} \}$ be the candidates and $a\textsubscript{i}$ and $b\textsubscript{i}$ be the candidate and solution incidence vectors. \\
\begin{align*}
d(A,B) &= \sum_{i=1}^{n}(a\textsubscript{i} + b\textsubscript{i} - 2a\textsubscript{i}b\textsubscript{i})\\
 &= \sum_{i=1}^{n}[(1-b\textsubscript{i})a\textsubscript{i} + (1-a\textsubscript{i})b\textsubscript{i}]\\
 &= \sum_{i=1}^{n}|a\textsubscript{i} - b\textsubscript{i}| = ||a - b||\textsubscript{1}
\end{align*}
\end{proof}
Therefore the Hamming Distance between the incidence vectors can act as a metric for mapping. A secondary measure utilized in the mapping is $\delta\textsubscript{B}(A)$ = $|A| - |A \cap B|$ which counts the number of candidates in set $A$ but not in set $B$. Stochastic convergence proof is discussed next.

@@

The implication of $d(F\textsubscript{t}, M\textsuperscript{*}) \rightarrow 0$ implies $\delta\textsubscript{M\textsuperscript{*}}(F\textsubscript{t}) \rightarrow 0$ extends to the worst case scenario of $n = M\textsuperscript{*}$. However, if a Markov Chain is maintained dynamically, $|M\textsuperscript{*}|=1$ and the limited population size will converge to a critical point. The rate of convergence is another important piece in this discussion.

\begin{theorem}
Let $n\textsubscript{i,t}$, $F$, $GM$ and $\lambda$ be the population of the $i\textsuperscript{th}$ department of DA at time $t$, fitness function, rate of cross-over-mutation and threshold for the memory element respectively. The rate of population progression from department $i$ to $j$ for a given problem can be expressed as

\begin{equation*}
\frac{d(Population\textsubscript{i $\rightarrow$ j})}{dt} \propto f(n\textsubscript{i,t}, \frac{1}{F}, GM, \lambda)
\end{equation*}
\end{theorem}

\begin{proof}\renewcommand{\qedsymbol}{}

Consider $n\textsubscript{i,t}$ and $F$ as a combined quantity $Q(i,j,t)$. The distribution of $Q(i,j,t)$ will be binomial as the peak is achived with maximum population and highest fitness score. The probability of candidate $c$ at department $i$ to continue into department $j$ at time $t+1$ will be given by

\begin{equation*}
P(j|i,t+1) =  {n\textsubscript{$i$,$t$} \choose n\textsubscript{$i$,$t$}} GM\textsuperscript{$n\textsubscript{$i$,$t$}$}
\end{equation*}

Based on this distribution, diffusion equations with initial state $p$, relative frequency of candidate selection till current department $\mu$ and selection strength $s$ can be written as:

\begin{equation*}
\frac{\partial \mu(p,t)}{\partial t} = \frac{p(1-p)}{2}\frac{\partial^2 \mu(p,t)}{\partial^2 p} + sp(1-p)\frac{\partial mu(p,t)}{\partial mu}
\end{equation*}

Fixing this probability when $t$ $\rightarrow$ $\infty$ as

\begin{equation*}
u(p) = \lim_{t \rightarrow \infty} {\partial(p,t)}
\end{equation*}

We get the rate of transition of a candidate as a function of the proficiency over time $t$, $u(p)\textsuperscript{$t$}$.
\end{proof}
% From a mathematical point of view, both the structure and the search processes evolve over time with feedback. For each search, a lookup is conducted by candidate $\textit{c}$ in table $\textit{H}$. If not found, a solution $\textit{x\textsubscript{0}}$ is assumed as the initial point and the search of optimum solution $\textit{x\textsubscript{1}}$ begins. At the end of each expedition, the top department's performance is graded through a reward system. Based on the global performance overall a set runtime, either the department continues in power or gets replaced.
